### 2018-03-20 Graduate - Introduction to Analysis II/HW4/4HW20180218.tex
add 5.2.2 d, e

\textbf{(d)}

>>>>

\textbf{(d)}
If $z = e^{2i\theta} $ then $\bar{z} = \frac{1}{z}$ and so
$$
a+\sin^2\theta = a-\frac{1}{4}(e^{2i\theta}+e^{-2i\theta}-2) = a-\frac{1}{4}(z+\bar{z}-2) = -\frac{z^2-(4a+2)z+1}{4z}.
$$
Hence
$$
\int_{0}^{\pi/2}\frac{d\theta}{a+\sin^2\theta} = \frac{1}{2}\int_{0}^{\pi}\frac{d\theta}{a+\sin^2\theta} = i\int_{\gamma}\frac{1}{z^2-(4a+2)z+1}dz,
$$
where $\gamma = \{|z| = 1\}$. But $z^2-(4a+2)z+1 = (z-z_1)(z-z_2) $ where $z_1 = (1+2a)+2\sqrt{a^2+a}, ~z_2 = (1+2a)-2\sqrt{a^2+a} $. Since $a > 0$ we know $|z_1| > 1 $ and $|z_2| < 1$, by residue theorem,
$$
\int_{\gamma}\frac{1}{z^2-(4a+2)z+1}dz = 2\pi iRes(f, z_1) = \frac{\pi i}{-2\sqrt{a^2+a}}.
$$
Hence
$$
\int_{0}^{\pi/2}\frac{d\theta}{a+\sin^2\theta} = \frac{\pi}{2\sqrt{a^2+a}}.
$$

\textbf{(e)}
Define $G, l(z), \gamma$ as in Example 2.10, then
$$
\int_{\gamma}\frac{l(z)}{(1+z^2)^2}dz = \int_{r}^{R}\frac{\log z}{(1+x^2)^2}dx +\int_{0}^{\pi}\frac{\log R +i\theta}{(1+R^2e^{2i\theta})^2}iRe^{i\theta}d\theta + \int_{-R}^{-r}\frac{\log |x|+\pi i}{(1+x^2)^2}dx + \int_{\pi}^{0}\frac{\log r +i\theta}{(1+r^2e^{2i\theta})^2}ire^{i\theta}d\theta
$$
by residue theorem,
$$
\int_{\gamma}\frac{l(z)}{(1+z^2)^2}dz = \frac{(\pi+2i)\pi i}{4}.
$$
First,
$$
\int_{r}^{R}\frac{\log z}{(1+x^2)^2}dx + \int_{-R}^{-r}\frac{\log |x|+\pi i}{(1+x^2)^2}dx = 2\int_{r}^{R}\frac{\log z}{(1+x^2)^2}dx + \frac{\pi i}{2}\left(\frac{R}{R^2+1}-\frac{r}{r^2+1}+\arctan R-\arctan r\right)
$$
and
$$
\left|\int_{0}^{\pi}\frac{\log R +i\theta}{(1+R^2e^{2i\theta})^2}iRe^{i\theta}d\theta\right| \le \frac{R|\log R|}{|1-R^2|^2}\int_{0}^{\pi}d\theta + \frac{R}{|1-R^2|^2}\int_{0}^{\pi}\theta d\theta \to 0,
$$
as $R\to \infty$. Also, we know $r\log r\to 0$ as $r\to 0^+ $, hence
$$
\left| \int_{\pi}^{0}\frac{\log r +i\theta}{(1+r^2e^{2i\theta})^2}ire^{i\theta}d\theta\right| \to 0.
$$
Hence,
$$
\int_{0}^{\infty}\frac{\log z}{(1+x^2)^2}dx = \frac{1}{2}\left(\frac{(\pi+2i)\pi i}{4}-\frac{\pi i}{2}\frac{\pi}{2}\right) = -\frac{\pi}{4}.
$$
